Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-12-20 Ben_Manuscripts/stochastic_transport/Draft.tex
Added missing figures

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. In Figure~\ref{fig:anticorrelated_hops}, we use Urea to
  support this claim. Analogous figures for all other solutes are presented in the Supporting
  Information, Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops}.
  The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
  summarized in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.

@@

  Using the approach described above, we validated our 1 and 2 mode models with
  urea and acetic acid, since their trajectories appear stationary. The 
  resultant MSD plots are shown in Figure~\ref{fig:train_test}. We consider 
  our models to match well if their predictions lie within the 1-$\sigma$
  confidence intervals of the MD MSDs. We also look for qualitative agreement
  in the shape of the curves.

@@

  This brief analysis suggests two shortcomings of the AD model. First, positional
  anti-correlation may diminish after a sufficiently long time lag, dependent on the 
  solute being studied. Second, it is difficult to reliably parameterize the Hurst
  parameter which is important for accurately describing the curvature of the solute
  MSDs.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE.pdf}
  \caption{Urea}\label{fig:1mode_msd_comparison_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_GCL.pdf}
  \caption{Ethylene Glycol}\label{fig:1mode_msd_comparison_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_MET.pdf}
  \caption{Methanol}\label{fig:1mode_msd_comparison_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH.pdf}
  \caption{Acetic Acid}\label{fig:1mode_msd_comparison_ACH}
  \end{subfigure}
  \caption{MSDs generated from realizations of our 1 mode anomalous diffusion models
  agree well with MD-generated data when using an exponential cutoff (sFBMcut and SFLMcut).
  When we do not apply an exponential cut-off to the dwell time distribution (sFBM 
  and SFLM), MSDs are underpredicted. Drawing hops from a truncated L\'evy stable 
  distribution results in higher MSDs than draws from Gaussians (sFLM and sFLMcut).}\label{fig:anomalous_msds_1mode}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE.pdf}
  \caption{Urea}\label{fig:2mode_msd_comparison_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_GCL.pdf}
  \caption{Ethylene Glycol}\label{fig:2mode_msd_comparison_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_MET.pdf}
  \caption{Methanol}\label{fig:2mode_msd_comparison_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH.pdf}
  \caption{Acetic Acid}\label{fig:2mode_msd_comparison_ACH}
  \end{subfigure}
  \caption{MSDs generated from realization of our 2-mode anomalous diffusion model
  also match well to MD-generated data. The MSD of urea appears to be underpredicted
  by all model combinations. The MSD of ethylene glycol is predicted well when 
  we draw dwell times from a power law distribution with an exponential cut-off.}\label{fig:anomalous_msds_2mode}
  \end{figure}

@@

  The 2 mode models shows considerably less curvature at large time lags than
  the 1 mode model because the implementation of the 2 mode model prevents long
  timescale correlation. The width of the hop distribution changes every time
  a switch between pores and tails occurs. We are unaware of an appropriate
  technique which can correlate hops that come from different hop distributions, 
  therefore every time a mode switch occurs, the correlation structure is 
  broken. Solutes which switch between modes the least show the greatest
  curvature. Methanol spends $> 90\%$ of its time in the tails, so mode transitions
  are relatively rare and the predicted MSD has curvature. This artificially
  solves the problem of long timescale correlation, however we do not recommend this
  as it has no theoretical basis.

@@

  We can use the 2 mode model to gain an even deeper understanding of solute behavior
  in the pore versus in the tails. It is clear that solutes are significantly slowed 
  while they are in the tail region where long dwell times are more probable
  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Interestingly, 
  $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
  structurally similar molecules, both planar with two heavy atoms attached to a 
  carbonyl group. Their small size and rigid shape may allow them to occasionally slip
  through gaps in the tails. Meanwhile, methanol is small enough that it does not need
  to make larger jumps to escape traps.

@@

  % BJC4: I moved this discussion up. It used to be after I presented the parameters
  % BJC5: The pore/tail percentages could potentially go in the previous section, with
  % the two-mode model.
  Solute size and chemical functionality influence which states are visited most frequently.
  In Figure~\ref{fig:state_probabilities}, we plotted the probabilities of occupying
  a given state at any time. Urea and acetic acid spend slightly more than half 
  their time in the tails (56\% and 62\% of their time respectively) while ethylene
  glycol spends about 44\% of its time in the tails. Urea and acetic acid's compact
  and flat structure allows it to more easily partition into the tails while ethylene
  glycol prefers the pore region due to its two hydrophilic hydroxyl groups. Meanwhile
  methanol spends 91 \% of its time in the tails likely due to its small size.

  \begin{figure}
  \centering
  \includegraphics[width=0.475\textwidth]{state_probabilities.pdf}
  \caption{Solutes spend varying amounts of time under the influence of each
  trapping mechanism. Methanol spends the majority of its time in the tail region
  while the rest of solute spend similar amounts of time in each region.}\label{fig:state_probabilities}
  \end{figure}

  Urea spends the largest fraction of its time trapped via association with sodium ions.
  It does so 31\% of the total time while in the tails (state 3) and 21\% of the
  total time while in the pores (state 7). The electron-dense and unshielded oxygen
  atom of urea's carbonyl group is prone to associate with positively charged sodium
  ions. The nitrogen atoms of urea are only weak hydrogen bond donors.

@@

  Methanol spends most of its time unbound in the tail region (state 1) and spends a 
  significant portion of time hydrogen bonded to while in the tail regions.
  Most of the tail region hydrogen bonds are donated from methanol to the ether
  linkages between the monomer head groups and tails.

@@

  To create an MSDDM for each solute, we determined the state sequence associated
  with each solute trajectory and then generated emission distributions of fluctuations
  within each state as well as transitions between states. There are not enough 
  consecutive observations of each type of transition with which to study their 
  individual correlation structures so we grouped all transition distributions
  into a single distribution and measured the correlation of the series of all 
  transitions. We lose information about individual types of transitions, however, 
  we believe this is unavoidable without at least an order of magnitude of additional data.
  In theory, one could parameterize separate transition distributions for those
  which occur in the tails versus in the pores, however this would lead to the same
  issues shown by the anomalous diffusion model.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{H_v_state.pdf}
  \caption{}\label{fig:H_v_state}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
  \caption{}\label{fig:sigma_v_state}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{alpha_v_state.pdf}
  \caption{}\label{fig:alpha_v_state}
  \end{subfigure}
  \caption{The parameters of the MSDDM are strong functions of trapping mechanisms.
  We observe different parameters bu with similar trends between the tail and pore
  region. The states are defined in Table~\ref{table:states}. To aid the reader, we 
  labeled each state with an abbreviation which identifies the combination of 
  conditions to which each solute is subject: t - tails, p - pores, h - hydrogen bonded, 
  a - associated with sodium. The legend in (a) applies to all subplots. (a) Motion is
  highly anti-correlated in trapped states. As the number of simultaneously influencing
  trapping mechanisms increases, the Hurst parameter decreases. The Hurst parameter is
  highest during transitions between states (state T). (b) As more trapping mechanisms
  simultaneously influence solutes, the width of the hop length distribution decreases.
  The largest hops occur when solutes are unbound in the pores. (c) The weight of the 
  hop length distribution's tails, parameterized by $\alpha_h$ increases as more trapping
  mechanisms influence solute simultaneously. The transition hop distributions have
  among the heaviest tails.}\label{fig:msddm_parameters}
  \end{figure}

@@

  As solutes are influenced by more trapping interactions simultaneously (i.e. hydrogen
  bonding \textit{and} associated with sodium versus just hydrogen bonding), the 
  width of the hop length distribution, $\sigma$, decreases while its L\'evy index,
  $\alpha_h$, increases. Treating states in the tail and pore regions independently, 
  $\sigma$ is largest and $\alpha_h$ is smallest when solutes are not hydrogen bonding
  or associating with sodium (states 1 and 5). Solutes are free to move and take 
  occasionally large hops. The smallest $\sigma$ and highest $\alpha_h$ values are
  measured when solutes are hydrogen bonding and associating with sodium at the
  same time (states 4 and 8). Motion is restricted by multiple tethers which 
  maintains a relatively narrow distribution of hop lengths.

@@

  In most cases, The MSDDM predicts the magnitude of the MD MSDs within their 
  1-$\sigma$ confidence intervals. Using the parameters shown in 
  Figure~\ref{fig:msddm_parameters}, we simulated 1000 MSDDM trajectory 
  realizations for each solute, as described in Section~\ref{method:MSMs},
  then calculated their MSDs (see Figure~\ref{fig:msddm_performance}). Methanol's
  MSD is over-predicted at short timescales while acetic acid's entire MSD 
  curve is severely over-predicted.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_msddm.pdf}
  \caption{Urea}\label{fig:URE_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_msddm.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_msddm.pdf}
  \caption{Methanol}\label{fig:MET_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_msddm.pdf}
  \caption{Acetic Acid}\label{fig:ACH_msddm}
  \end{subfigure}
  \caption{In most cases, the magnitude of the MSD curves predicted by the 
  MSDDM agree well with those generated from MD simulations. The predicted MSD
  curves of urea and ethylene glycol lie within the 1-$\sigma$ confidence 
  intervals of MD for all time lags. Methanol under-predicts the MSD at small
  time lags and acetic acid grossly over-predicts the MSD at all time lags.
  Like the anomalous diffusion model, the MSDDM doesn't fully capture the 
  curvature of the MD MSD curves. }\label{fig:msddm_performance}
  \end{figure}

  The dynamics of urea, ethylene glycol and, to a lesser extent, methanol 
  appear to be well-captured by the MSDDM. One could argue that the curves
  of ethylene glycol and urea are statistically indistinguishable. However, 
  it's possible that they may diverge on longer timescales due to differences
  in their curvature. Similarly, methanol's MD MSD is nearly linear while 
  the MSDDM prediction is curving downward implying that it may underestimate
  the MSD on longer timescales.

  The predicted MSD of acetic acid is severely over-estimated most likely due
  to poor parameterization. Acetic acid has a transitional Hurst parameter 
  $\sigma$ values that are very similar to Urea. Consequently, the final 
  magnitude of acetic acid's MSD actually lies just within the lower bound
  of Urea's MD MSD 1-$\sigma$ confidence interval.

  The MSDDM suffers similar shortcomings to the AD model. First, curvature 
  on long timescales due to positional anti-correlation may result in 
  underestimates of the MSD at large time lags. As suggested earlier, truncating
  the positional autocorrelation function may help solve this issue. Second, 
  parameterization can be challenging.

  The MSDDM offers mechanistic insight and, in 3 out of 4 cases, gives reasonable
  predictions of solute MSDs. We can used the MSDDM to obtain a detailed picture of dynamics within
  each state in terms of the magnitude of their fluctuations and correlation with previous 
  motion.

@@

  We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
  diffusion model in order to demonstrate how one can use its realizations in
  order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
  parameters extracted from MD simulations. The sFLMcut AD model and MSDDM yield 
  similar predictions at a much greater computational cost due to the slow
  generation of fractional L\'evy noise.
  %MRS5: One question is if other method would lead to substantially
  %different results for fluxes or selectivity.  May need too think
  %about justification more if just one method is mentioned.
  %BJC5: would love to test MSDDM against this but I don't know how to make 
  % the algorithm faster. It already uses an FFT to correlate the data (to which I pass powers of 2)

@@

  %BJC4: not sure if the next couple paragraphs belong in methods 
  %MRS5: this could potentially be in methods.  Alternatives can be discussed there.
  %BJC5: I tried putting this in methods, but it feels weird without stating the
  % empirical equation. And I'm avoiding stating the empirical model in the methods
  % since it is informed by the data.
  It is computationally infeasible to simulate trajectories long enough that they
  traverse the length of a macroscopic pore. To date, the thinnest H\textsubscript{II}
  LLC membrane synthesized with the monomer in this work was 7$\mu$m thick. Using
  24 cores to simulate trajectory realizations in parallel, it takes on the order 
  of 1 day to simulate 10000 realizations of solutes traversing a 50 nm pore. The 
  RAM requirements and performance scales greater than linearly and thus would 
  take an infeasible amount of memory and time to simulate transport through a 
  pore over 100 times longer.

>>>>

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. In Figure~\ref{fig:anticorrelated_hops}, we use Urea to
  support this claim. Analogous figures for all other solutes are presented in the Supporting
  Information, Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops}.
  The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  %The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
  %summarized in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.

@@

  Using the approach described above, we validated our 1 and 2 mode models with
  urea and acetic acid, since their trajectories appear stationary. In 
  Figure~\ref{fig:ad_eyetest}, we show that realizations of the AD model appear
  qualitatively similar to those seen in our MD simulations (Figure~\ref{fig:solute_trajectories}).
  The MSDs resulting from 1000 realizations of the AD model are shown in 
  Figure~\ref{fig:train_test}. We consider the model's prediction to match well if the
  MSD lies within the 1-$\sigma$ confidence intervals of the MD MSDs. We also
  look for qualitative agreement in the shape of the curves.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{ad_realizations_1mode.pdf}
  \caption{Simulations of 1 mode AD model trajectories for Urea display 
  qualitatively similar hopping and trapping behavior to that shown in 
  Figure~\ref{fig:solute_trajectories}. Analogous plots are shown for other solutes
  %BJC5: todo: add plots to SI. Show I add a 2 mode model plot?
  and the 2 mode mdoel in the Supporting Information. Dwell times may be exaggerated in the
  sFBM and sFLM models because the power law dwell time distributions have infinite
  variance.}\label{fig:ad_eyetest}
  \end{figure}

@@

  This brief qualitative analysis suggests two shortcomings of the AD model. First, 
  positional anti-correlation may dissipate after a sufficiently long time lag, dependent on the 
  solute being studied. Second, it is difficult to reliably parameterize the Hurst
  parameter which is important for accurately describing the curvature of the solute
  MSDs.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE.pdf}
  \caption{Urea}\label{fig:1mode_msd_comparison_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_GCL.pdf}
  \caption{Ethylene Glycol}\label{fig:1mode_msd_comparison_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_MET.pdf}
  \caption{Methanol}\label{fig:1mode_msd_comparison_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH.pdf}
  \caption{Acetic Acid}\label{fig:1mode_msd_comparison_ACH}
  \end{subfigure}
  \caption{In most cases, MSDs generated from realizations of our 1 mode anomalous
  diffusion models agree well with MD-generated data when using an exponential cutoff
  on the dwell time distribution (sFBMcut and SFLMcut). When we do not apply an 
  exponential cut-off (sFBM and SFLM), MSDs are underpredicted. Drawing hops from a
  truncated L\'evy stable distribution yields MSDs similar to when hops are drawn 
  from Gaussian disributions (sFLM and sFLMcut).}\label{fig:anomalous_msds_1mode}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE.pdf}
  \caption{Urea}\label{fig:2mode_msd_comparison_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_GCL.pdf}
  \caption{Ethylene Glycol}\label{fig:2mode_msd_comparison_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_MET.pdf}
  \caption{Methanol}\label{fig:2mode_msd_comparison_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH.pdf}
  \caption{Acetic Acid}\label{fig:2mode_msd_comparison_ACH}
  \end{subfigure}
  \caption{MSDs generated from realizations of our 2-mode anomalous diffusion model
  predict the magnitude of the MSDs to a similar degree of accuracy as the 1 mode
  model. Relative to the predictions of the 1 mode model the MSDs lack curvature because
  the hop correlation structure is broken every time a transition between tails occurs.}\label{fig:anomalous_msds_2mode}
  \end{figure}

@@

  The 2 mode models shows considerably less curvature at large time lags than
  the 1 mode model because the implementation of the 2 mode model prevents long
  timescale correlation. The width of the hop distribution changes every time
  a switch between pores and tails occurs. We are unaware of an appropriate
  technique which can correlate hops that come from different hop distributions, 
  therefore every time a mode switch occurs, the correlation structure is 
  broken. Solutes which switch between modes the least show the greatest
  curvature. Methanol spends $> 90\%$ of its time in the tails, so mode transitions
  are relatively rare and the predicted MSD has significant curvature. This artificially
  solves the problem of long timescale correlation, however we do not recommend this
  as it has no theoretical basis.

@@

  We can use the 2 mode model to gain an even deeper understanding of solute behavior
  in the pore versus in the tails. It is clear that solutes are significantly slowed 
  while they are in the tail region where long dwell times are more probable
  (smaller $\alpha_d$) and hops are smaller (smaller $\sigma$). Each solute spends 
  a different amount of time in the tails (see Figure~\ref{fig:AD_mode_occupation}). 
  Urea and acetic acid spend slightly more than half of their time in the tails 
  (56\% and 62\% of their time respectively) while ethylene glycol spends about 
  44\% of its time in the tails. Urea and acetic acid's compact and flat structure 
  allows it to more easily partition into the tails while ethylene glycol prefers
  the pore region due to its two hydrophilic hydroxyl groups. Meanwhile methanol 
  spends 91 \% of its time in the tails likely due to its small size.  
  The value of $\alpha_h$ for urea and acetic acid in the tails is 1.50 meaning its hop distribution
  is heavy tailed relative to ethylene glycol and methanol whose $\alpha_h$ values are
  more consistent with a Gaussian distribution ($\alpha$=2). Acetic acid and urea are
  structurally similar molecules, both planar with two heavy atoms attached to a 
  carbonyl group. Their small size and rigid shape may allow them to occasionally slip
  through gaps in the tails. Meanwhile, methanol is small enough that it does not need
  to make larger jumps to escape traps.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{AD_mode_occupation.pdf}
  \caption{Solutes spend various amounts of time in the tail and pore region dependent
  on their size, shape and chemical functionality. Methanol's small size favors 
  occupation of the much larger accessible volume in the tails. Urea and acetic acid
  are fairly stable in both regions since they are small and hydrophilic. Ethylene 
  glycol is has a slight preference for the pores likely because it is a larger
  molecule with two hydrophilic hydroxyl groups.}\label{fig:AD_mode_occupation}
  \end{figure}

@@

  % BJC4: I moved this discussion up. It used to be after I presented the parameters
  Solute size and chemical functionality influence which states are visited most frequently.
  In Figure~\ref{fig:state_probabilities}, we plotted the probabilities of occupying
  a given state at any time. Solutes tend to favor the same types of interactions 
  independent of which region they are in.

  % BJC5: moved to previous section  
%   Urea and acetic acid spend slightly more than half of
%  their time in the tails (56\% and 62\% of their time respectively) while ethylene
%  glycol spends about 44\% of its time in the tails. Urea and acetic acid's compact
%  and flat structure allows it to more easily partition into the tails while ethylene
%  glycol prefers the pore region due to its two hydrophilic hydroxyl groups. Meanwhile
%  methanol spends 91 \% of its time in the tails likely due to its small size.

  \begin{figure}
  \centering
  \includegraphics[width=0.475\textwidth]{state_probabilities.pdf}
  \caption{Solutes spend varying amounts of time under the influence of each
  trapping mechanism. To aid the reader, we labeled each state with an abbreviation which
  identifies the combination of conditions to which each solute is subject in each state:
  t - tails, p - pores, h - hydrogen bonded, a - associated with sodium. Solutes tend to 
  favor the same types of interactions (e.g. hydrogen bonding and/or associating with sodium
  ions) independent of whether they are in the pores or the tails.}\label{fig:state_probabilities}
  \end{figure}

  Urea spends the largest fraction of its time trapped via association with sodium ions.
  It does so 31\% of the total time while in the tails (state 3) and 21\% of the
  total time while in the pores (state 7). Note that sodium does not drift significantly 
  into the tails but sits close to the pore/tail region boundary. The electron-dense 
  and unshielded oxygen atom of urea's carbonyl group is prone to associate with 
  positively charged sodium ions. The nitrogen atoms of urea are only weak hydrogen bond
  donors.

@@

  Methanol spends most of its time unbound in the tail region (state 1) and spends a 
  significant portion of time hydrogen bonded while in the tail regions.
  Most of the tail region hydrogen bonds are donated from methanol to the ether
  linkages between the monomer head groups and tails.

@@

  To create an MSDDM for each solute, we determined the state sequence associated
  with each solute trajectory and then generated emission distributions of fluctuations
  within each state as well as transitions between states. There are not enough 
  consecutive observations of each type of transition with which to study their 
  individual correlation structures so we grouped all transition distributions
  into a single distribution and measured the correlation of the series of all 
  transitions. We lose information about individual types of transitions, however, 
  we believe this is unavoidable without at least an order of magnitude of additional data.
  In theory, one could parameterize separate transition distributions for those
  which occur in the tails versus in the pores, however this would lead a broken 
  correlation structure similar to that seen in the 2 mode AD model.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{H_v_state.pdf}
  \caption{}\label{fig:H_v_state}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
  \caption{}\label{fig:sigma_v_state}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{alpha_v_state.pdf}
  \caption{}\label{fig:alpha_v_state}
  \end{subfigure}
  \caption{The parameters of the MSDDM are strong functions of trapping mechanisms.
  We observe different parameters but with similar trends between the tail and pore
  region. The states are defined in Table~\ref{table:states}. See Figure~\ref{fig:state_probabilities}
  for a description of the abbreviation under each state number. The legend in (a) applies to all subplots. (a) Motion is
  highly anti-correlated in trapped states. As the number of simultaneously influencing
  trapping mechanisms increases, the Hurst parameter decreases. The Hurst parameter is
  highest during transitions between states (state T). (b) As more trapping mechanisms
  simultaneously influence solutes, the width of the hop length distribution decreases.
  The largest hops occur when solutes are unbound in the pores. (c) The weight of the 
  hop length distribution's tails, parameterized by $\alpha_h$ increases as more trapping
  mechanisms influence solute simultaneously. The transition hop distributions have
  among the heaviest tails.}\label{fig:msddm_parameters}
  \end{figure}

@@

  As solutes are influenced by more trapping interactions simultaneously (e.g.~hydrogen
  bonding \textit{and} association with sodium versus just hydrogen bonding), the 
  width of the hop length distribution, $\sigma$, decreases while its L\'evy index,
  $\alpha_h$, increases. Treating states in the tail and pore regions independently, 
  $\sigma$ is largest and $\alpha_h$ is smallest when solutes are not hydrogen bonding
  or associating with sodium (states 1 and 5). Solutes are free to move and take 
  occasionally large hops. The smallest $\sigma$ and highest $\alpha_h$ values are
  measured when solutes are hydrogen bonding and associating with sodium at the
  same time (states 4 and 8). Motion is restricted by multiple tethers which 
  maintains a relatively narrow distribution of hop lengths.

@@

  Qualitatively, realizations of the MSDDM are not consistent with MD solute
  trajectories. Using the parameters shown in Figure~\ref{fig:msddm_parameters}
  we generated realizations of the MSDDM and plotted a typical realization for each
  solute in Figure~\ref{fig:msddm_eyetest}. Except in rare cases, the solutes do not make
  large hops. There are two reasons for this behavior. First, the width of 
  hop length distributions are much smaller than those of the AD model. Closer
  examination of Figure~\ref{fig:solute_trajectories} reveals that hops tend
  to be an accumulation of a series of hops in the same direction. All of the 
  hops in the MSDDM are negatively correlated which prevents this from happening.
  The second reason is a consequence of using a single hop length distribution 
  for transitions. Many transitions occur between two trapped states where the 
  transitional hops are actually very small. Our model ignores this physical 
  restriction which can cause the solute to drift rather than stay trapped.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{msddm_realizations.pdf}
  \caption{Realizations of the MSDDM for each solute do not reproduce the hopping
  and trapping behavior observed in our MD simulations. Except for a few large 
  hops, the trajectories are qualitatively similar to what one might expect for
  Brownian motion. Note that the length of the realizations are equal to the length
  of the equlibrated portion of the MD trajectories for each solute.}\label{fig:msddm_eyetest}
  \end{figure}

  %Methanol's
  %MSD is over-predicted at short timescales while acetic acid's entire MSD 
  %curve is severely over-predicted.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_msddm.pdf}
  \caption{Urea}\label{fig:URE_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_msddm.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_msddm.pdf}
  \caption{Methanol}\label{fig:MET_msddm}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_msddm.pdf}
  \caption{Acetic Acid}\label{fig:ACH_msddm}
  \end{subfigure}
  \caption{In most cases, the magnitude of the MSD curves predicted by the 
  MSDDM agree well with those generated from MD simulations. The predicted MSD
  curves of urea and ethylene glycol lie within the 1-$\sigma$ confidence 
  intervals of MD for all time lags. Methanol over-predicts the MSD at small
  time lags and acetic acid grossly over-predicts the MSD at all time lags.
  Like the anomalous diffusion model, the MSDDM doesn't fully capture the 
  curvature of the MD MSD curves. }\label{fig:msddm_performance}
  \end{figure}

  Despite qualitative differences in trajectory realizations, the dynamics of 
  urea, ethylene glycol and, to a lesser extent, methanol appear to be well-captured
  by the MSDDM. We simulated 1000 MSDDM trajectory realizations for each solute, as
  described in Section~\ref{method:MSMs}, then calculated their MSDs (see 
  Figure~\ref{fig:msddm_performance}). In most cases, the MSDDM predicts the magnitude of the MD MSDs 
  within their 1-$\sigma$ confidence intervals. One could argue that the curves
  of ethylene glycol and urea are statistically indistinguishable. However, 
  it's possible that they may diverge on longer timescales due to differences
  in their curvature. Similarly, methanol's MD MSD is nearly linear while 
  the MSDDM prediction is curving downward implying that it may underestimate
  the MSD on longer timescales.

  The predicted MSD of acetic acid is severely over-estimated most likely due
  to poor parameterization. As stated earlier, most of a solute's motion is 
  due to displacements during state transitions. Acetic acid has a transitional
  Hurst parameter close to Urea's and a transitional $\sigma$ value that 
  is higher than urea's. This suggests that the heavier tails of urea's transitional
  hop distribution (greater $\alpha_h$ value) are in large part responsible for 
  urea's higher predicted MSD. Although we note that acetic acid's predicted MSD
  actually lies just within the lower bound of Urea's MD MSD 1-$\sigma$ 
  confidence interval. There is also the strong possibility that the over-estimate is
  a consequence of lumping together all of acetic acid's transitional hops into
  a single correlated distribution.

  The MSDDM suffers similar shortcomings to the AD model. First, curvature 
  on long timescales due to positional anti-correlation may result in 
  underestimates of the MSD at large time lags. As suggested earlier, truncating
  the positional autocorrelation function may help solve this issue. Second, 
  parameterization can be challenging. In addition to possibly poor estimates 
  of the Hurst parameter, we made the simplifying assumption that we could lump
  all transitional hops into a single distribution. While this appears to work
  in most cases, it is the source of qualitative mismatches between MSDDM
  realations and MD simulation trajectories and it may be the source of the 
  over-estimate of acetic acid's MSD.

  The MSDDM offers mechanistic insight and, in 3 out of 4 cases, gives reasonable
  predictions of solute MSDs. To successfully apply the model, one must know 
  representative discrete states beforehand or apply some technique to identify
  them. At the very least, we can used the MSDDM to obtain a detailed quantitative
  picture of dynamics within each state in terms of the magnitude of their 
  fluctuations and correlation with previous motion. If we have confidence in
  their predictive ability, then we can project solute trajectories out to 
  macroscopic timescales and estimate macroscopic observables such as solute 
  flux and selectivity.

@@

  We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
  diffusion model and the MSDDM in order to demonstrate how one can use their realizations
  in order to calculate the flux (section~\ref{method:mfpt}) of solutes given model 
  parameters extracted from MD simulations. The 1-mode sFBMcut mode generates predictions
  similar to the 1-mode sFLMcut model at a lower computational cost and is far more
  accurate than sFBM and sFLM. The 2-mode model has a broken correlation structure, so 
  we do not consider it here.

  %MRS5: One question is if other method would lead to substantially
  %different results for fluxes or selectivity.  May need too think
  %about justification more if just one method is mentioned.
  %BJC5: Added MSDDM

@@

  %BJC4: not sure if the next couple paragraphs belong in methods 
  %MRS5: this could potentially be in methods.  Alternatives can be discussed there.
  %BJC5: I tried putting this in methods, but it feels weird without stating the
  % empirical equation. And I'm avoiding stating the empirical model in the methods
  % since it is informed by the data.
  It is computationally infeasible to simulate trajectories long enough that they
  traverse the length of a macroscopic pore. To date, the thinnest H\textsubscript{II}
  LLC membrane synthesized with the monomer in this work was 7$\mu$m thick. Using
  24 cores to simulate trajectory realizations in parallel, it takes on the order 
  of 1 day to simulate 10000 sFBMcut realizations of solutes traversing a 50 nm pore.
  The computational requirements of the MSDDM are about 10 times longer. For both
  models, the RAM requirements and performance scales greater than linearly and 
  thus would take an infeasible amount of memory and time to simulate transport 
  through a pore over 100 times longer.
